Getting mortality from atlantisom: testing calc_Z function II

### 2019-06-12 TestCalcZ2.Rmd
further alignment of outputs

@@

  # align model output timesteps (days) with recruitment periods (days)
  numstime.days <- unique(nums$time)*toutinc
  # Sum numbers output over all boxes/depth/cohorts
  totnums <- aggregate(atoutput ~ species + time, data = nums, sum) %>%
    mutate(time.days = time*toutinc) %>%
    mutate(yr = floor(time.days/365))

@@

    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[numstime.days[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[numstime.days[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- numstime.days[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(numstime.days[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        totnums$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

@@

>>>>

  #Isaac determined that yr 0 (Time 0) in the YOY file is not real, don't use it
  #below assigns year 1 to times 0:stepperyr, all good output timesteps in truth$nums

@@

  # align model output timesteps (days) with recruitment periods (days)
  #numstime.days <- unique(nums$time)*toutinc
  # Sum numbers output over all boxes/depth/cohorts
  totnums <- aggregate(atoutput ~ species + time, data = nums, sum) %>%
    mutate(time.days = (time+1)*toutinc) %>% #makes time 0 into days 0->73, etc
    mutate(yr = ceiling(time.days/365))  # yr 1 is 0:stepsperyr to match recruits yr1
    #mutate(yr = floor(time.days/365)) # includes 0 value, yr 1 is

@@

    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[totnums$time.days[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[totnums$time.days[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- totnums$time.days[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(totnums$time.days[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        totnums$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

@@

Two approaches: sum nums each year, calculate survival between years (minus annual recruitment), turn into annual Z, or multiply timestep Zs to get annual?
